A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2015-11-23 docs/results_photometry_v3.02.tex
Edited dynamical modelling results sections.

@@

\paragraph{MGE for the inner regions.} We fit a MGE to J1331's smooth central region within $\sim 5''$ from the HST/WFPC2/WF3/F814W image (Figure \ref{fig:F814W}). Bright objects close to the bulge (blobs possibly belonging to the background galaxy and parts of the foreground spiral arm) were masked during the fit. J1331's galaxy center, position angle and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment. The MGE fit splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Equation \eqref{eq:MGEgeneral} convolved with the PSF MGE in Table \ref{tab:PSFMGEF814W} to it. The best fit MGE (PSF convolved) is compared to the data in Figure \ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in Table \ref{tab:MGEF814W}. The fit is a very good representation of the light distribution in the inner $5''$, but underestimates the light distribution outward.

@@

%============================================================================
\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\columnwidth]{fig/1331F814Wsci_MGE_M.ps}
  \caption{MGE for J1331's inner regions.}
 \label{fig:MGEinnerRegions}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
  \caption{MGE for J1331's outer regions.}
 \label{fig:MGEouterRegions}
\end{subfigure}%
\caption{MGEs for J1331's surface brightness distribution. Comparison of contours with constant F814W surface brightness (orange lines) with the corresponding iso-brightness contours of the best fit MGE, convolved with the PSF in Table \ref{tab:MGEF814W}, (gray lines). The black line has a length of $10''$ and it's orientation corresponds to the galaxy's position angle as found in Table \ref{tab:galaxyparameters}. For comparison the Einstein radius as found in Table \ref{tab:bestfitlensmodel}  is indicated as red dashed line. \emph{Panel (a)} Central regions of J1331. The MGE model is a good representation of the galaxy's light distribution along the major axis within $\sim 5''$. Its parameters are given in Table \ref{tab:MGEF814W}. This MGE is used as model for the stellar tracer distribution in the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}. \emph{Panel (b)} Outer regions of J1331. The orange lines indicate here contours of a smooth IRAF \emph{ellipse} fit to J1331 in the F814W filter; the gray lines are the corresponding best fit MGE. The green box corresponds to the image section shown in Panel (a). This MGE is not used for dynamical modelling, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms). We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions.}
\end{figure*}
%============================================================================

@@

%============================================================================
\begin{table*}
\centering
\caption{J1331's F814W MGE: Parameters of the best fit MGE to the F814W surface brightness of J1331 in Figure \ref{fig:F814W}. The fit is best inside an radius of $5''$. The galaxy center and position angle, which gives the orientation of the MGE with respect to the original image, are given in Table \ref{tab:galaxyparameters}. This MGE is used in the dynamical modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.  The first column gives the total F814W luminosity of the Gaussian in Equation \eqref{eq:centralItotalL} in units of counts. The second column is the corresponding I-band peak surface brightness in Equation \eqref{eq:MGEgeneral} in units of a luminosity surface density, calculated from the first column following the procedure described in Section \ref{sec:MGE_results}. The third and fourth column give the dispersion and the last column the axis ratio of the Gaussian in Equation \eqref{eq:MGEgeneral}.}
\begin{tabular}{cccccc}
\hline
 & total luminosity  & surface density & \multicolumn{2}{c}{Gaussian dispersion} & axis ratio\\
$i$  & $L_i$ [counts] & $I_{0,i}$ [$L_\odot$/pc$^2$] & $\sigma_i$ [$''$] & $\sigma_i$ [kpc] & $q'_i$\\\hline
1  &     9425.96 &      20768.  &  0.051   & 0.103  & 1.00\\
2  &    13173.0 &        3161.2 &  0.178   & 0.358  & 0.76\\
3  &    40235.0 &        1588.2 &  0.503   & 1.008  & 0.58\\
4  &    67755.2 &         502.25&  1.180   & 2.368  & 0.56\\
5  &    203677. &         136.51&  3.891   & 7.805  & 0.57\\\hline
\end{tabular}
\label{tab:MGEF814W}
\end{table*}
%============================================================================

>>>>

%============================================================================
\begin{table}
\centering
\caption{Galaxy Parameters of J1331.}
\begin{tabular}{lllr}
\hline
redshift \citep{SWELLSIII}                 & $z_d$ & 0.113 \\
angular diameter distance & $D_d$ [Mpc] & 414 \\
scaling                   & 1 kpc / 1 $''$ & 2.006 \\
position angle from North          & $\phi$ [degrees] & $42.90^\circ$\\
average axis ratio & $q'$ & 0.598\\
average ellipticity & $\epsilon = 1 - q'$ & 0.402 \\
apparent I-band magnitude & $m_\text{I}$ [mag] & 15.77 \\
total I-band luminosity & $L_\text{tot,I}$ [$10^{10} L_\odot$] & 5.6 \\
effective half-light radius & $R_\text{eff}$ [$''$] & 2.6 \\
& $R_\text{eff}$ [pc]& 5.2 & \\
\hline
\end{tabular}
\label{tab:galaxyparameters}
\end{table}
%============================================================================

@@

\paragraph{MGE for the inner regions.} We fit a MGE to J1331's smooth central region within $\sim 5''$ from the HST/WFPC2/WF3/F814W image (Figure \ref{fig:F814W}). Bright objects close to the bulge (blobs possibly belonging to the background galaxy and parts of the foreground spiral arm) were masked during the fit. J1331's galaxy center, position angle (with respect to North through East) and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment. The MGE fit splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Equation \eqref{eq:MGEgeneral} convolved with the PSF MGE in Table \ref{tab:PSFMGEF814W} to it. The best fit MGE (PSF convolved) is compared to the data in Figure \ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in Table \ref{tab:MGEF814W}. The fit is a very good representation of the light distribution in the inner $5''$, but underestimates the light distribution outward.

@@

%============================================================================
\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\columnwidth]{fig/1331F814Wsci_MGE_M.ps}
  \caption{MGE for J1331's inner regions.}
 \label{fig:MGEinnerRegions}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
  \caption{MGE for J1331's outer regions.}
 \label{fig:MGEouterRegions}
\end{subfigure}%
\caption{MGEs for J1331's surface brightness distribution. Comparison of contours with constant F814W surface brightness (orange lines) with the corresponding iso-brightness contours of the best fit MGE, convolved with the PSF in Table \ref{tab:MGEF814W}, (gray lines). The black line has a length of $10''$ and it's orientation corresponds to the galaxy's position angle as found in Table \ref{tab:galaxyparameters}. For comparison the Einstein radius as found in Table \ref{tab:bestfitlensmodel}  is indicated as red dashed line. \emph{Panel (a)} Central regions of J1331. The MGE model is a good representation of the galaxy's light distribution along the major axis within $\sim 5''$. Its parameters are given in Table \ref{tab:MGEF814W}. This MGE is used as model for the stellar tracer distribution in the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}. \emph{Panel (b)} Outer regions of J1331. The orange lines indicate here contours of a smooth IRAF \emph{ellipse} fit to J1331 in the F814W filter; the gray lines are the corresponding best fit MGE. The green box corresponds to the image section shown in Panel (a). This MGE is not used for dynamical modelling, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms). We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions. \Wilma{[TO DO: No dotted line]}}
\end{figure*}
%============================================================================

%============================================================================
\begin{table*}
\centering
\caption{Parameters of the best fit MGE to the F814W surface brightness of J1331 in Figure \ref{fig:MGEinnerRegions}. The fit is best inside an radius of $5''$. The position angle is given in Table \ref{tab:galaxyparameters}. This MGE is used in the dynamical modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}. The first column gives for each Gaussian the total F814W luminosity in Equation \eqref{eq:centralItotalL} in units of counts. The second column is the corresponding I-band peak surface brightness in Equation \eqref{eq:MGEgeneral} in units of a luminosity surface density. The third and fourth column give the dispersion and the last column the axis ratio of the Gaussian in Equation \eqref{eq:MGEgeneral}.}
\begin{tabular}{cccccc}
\hline
 & total luminosity  & surface density & \multicolumn{2}{c}{Gaussian dispersion} & axis ratio\\
$i$  & $L_i$ [counts] & $I_{0,i}$ [$L_\odot$/pc$^2$] & $\sigma_i$ [$''$] & $\sigma_i$ [kpc] & $q'_i$\\\hline
1  &     9425.96 &      20768.  &  0.051   & 0.103  & 1.00\\
2  &    13173.0 &        3161.2 &  0.178   & 0.358  & 0.76\\
3  &    40235.0 &        1588.2 &  0.503   & 1.008  & 0.58\\
4  &    67755.2 &         502.25&  1.180   & 2.368  & 0.56\\
5  &    203677. &         136.51&  3.891   & 7.805  & 0.57\\\hline
\end{tabular}
\label{tab:MGEF814W}
\end{table*}
%============================================================================

@@
